The imprint of global magma oceans on exoplanet demographics

### 2023-03-20 src/tex/ms.tex
discuss occurrence model caveats
* occurrence model caveats

* Edit, provide context to occurrence rate discussion

* change wording after review & discussion

---------
merges PR  #9

Co-authored-by: Martin Schlecker <martin.schlecker@mailbox.org>

>>>>

\subsubsection{Structures in the planet occurrence rate density}
In principle, the baseline occurrence rate density in radius-period space that governs the generation of our synthetic planet sample might influence our findings, especially if it contains any features that coincide with the injected demographic feature.
This is not the case in the model from \citet{Bergsten2022} that we adopted: Its occurrence rate density varies smoothly in the domain relevant for the runaway greenhouse hypothesis; transitions only occur at smaller instellations ($< \SI{50}{\watt\per\meter\squared}$) and larger radii ($> 1.6\,R_\oplus$).
We thus do not expect the model underlying our planet sample to affect the recovery of the transition.
However, it should be kept in mind that any unknown sharp features in the true distribution of terrestrial planets could complicate a detection or lead to a false positive result (see Sect.~\ref{sec:dis_falsepositive}).
